Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
memorability & believability findings done

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
% semantic vs episodic memory
% mention distance categories in the beginning (up up up) + everything else 
\section{Findings}
The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos. We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.

Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

@@

\section{Memorability}
Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory. To find out what features make a digital memory memorable, we examined participant responses to whether or not they were able to remember the location shown in a photo or recall the trip portrayed by a Rewind. Photo memorability is determined by whether or not the participant remembered the location depicted in a photo. Because a Rewind contains many locations, it would be unfair to evaluate the memorability of Rewind based on whether the participant remembers any locations in the Rewind. If participants do not recognize some depicted locations, they still have many other chances to pick out locations they remember. So, Rewind memorability is determined by whether or not the participant remembered and could distinguish the particular trip portrayed in a Rewind. In this section, we will look at differences in photo and Rewind memorability based on the five metrics discussed previously.

% h - deleted participants # for consistencies - P4, P6 and P10 for future reference
\subsubsection{Rewinds vs. Static Photos} 
Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$). When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time. Recognition rate of locations reached 96.6\% when participants were shown the accompanying Rewind. As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues. Three participants (P4, P6, and P10) who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind. They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' Further differences between Rewinds and static photos are discussed in the following sections.
%TODO h - add another table, only abt memorability tho

\subsubsection{Distance}
%TODO  where is home? need to explain this part in system? make sure this is explained
% only affect location rememberance
% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
The depicted location's distance away from the participant’s home had differing effects on photo memorability and Rewind memorability. Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.

For photos, as the distance increased, memorability decreased, suggesting that locations further away from home were less likely to be remembered. In Distance Group 0, or the participant's home location, location recall was 100\%. One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' Further away in Distance Group 1, remembrance dropped to 75\%, then later down to 10\% for Distance Group 5, which represented the locations furthest away from home. These percentages are statistically significant, with a p-value of 0.0028.

%TODO find citation that humans travel most within x km of their home/work nodes
%TODO memory competition--similar memories compete for significance
For Rewind memorability, there was no statistical significance. Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home in Distance Group 1. While remembrance for all distance groups was between 50--60\%, remembrance for Rewinds in Distance Group 1 was 25\%. This data suggests that participants often did not remember or could not distinguish the exact trips that occurred in locations close to their home. This is where most trips happen, and therefore competition between similar memories would make it harder for a person to distinguish the specific trip they were on that generated the Rewind.

@@

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
Differences in photo memorability due to visit frequency were statistically significant, while differences in location memorability were not. Photo memorability is higher for locations that are most frequently visited by the participant, with a remembrance rate of 72.3\%. Photo remembrance rate for the least frequently visited locations is 35.8\%. This is statistically significant at $\chi^2(1,128) = 14.458$, $p < 0.01$.

Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\% $\chi^2(1, N=20) = 3.215$, $p <.05$; and for least frequently visited locations Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p <.01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.

\subsubsection{GPS Usage}
Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p =.0715 (<.1)$. 
% h - prob explain this a little bit more
% Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance. (GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - come back to this if time allows
% because memories are simply not encoded so there's no way to retrieve it in the first place?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1, N=179) = 8.734$, $p <.01$), but does not impose significant effects on trip remembrance $\chi^2(1, N=177) = 0.713$, $p >.05$).  When asked whether they remember the location in a static photo, non-regular GPS users gave a positive answer 58\% of the time whereas regular GPS users gave a positive answer 33\% of the time. Although the difference between non-regular and regular GPS users' trip remembrance is not statistically significance, the between-subject percentage values still lean towards the observation that it is perhaps easier for non-GPS users to recall episodic memories from external memory cues, given that the total trip remembrance rate for non-GPS users is 48\% and that of GPS users is 56\%. Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, they may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations. One non-regular GPS user mentioned that ``I identify by landmarks'', yet this is something that regular GPS users may pay less attention to. \\

\subsubsection{Frequent Travelers}
% has no siginifant effects on location no trip rememberance
% needing explaination perhaps?
Although location rememberance is slightly higher for frequent traveler (51\% for frequent and 48\% for non-frequent), and trip rememberance is slightly higher for non-frequent traveler (53\% for frequent and 54\% for non-frequent), our study has not found these variances statistically significant.

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route". Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Believability}
Rewinds should be believable as memories, and be able to serve as digitally-sourced memories of locations and trips. For that purpose, we define the believability of a Rewind as its accuracy to the participant's memories. Here we will look at how GPS usage and visit frequency affect participants' believability judgments, and discuss the features that participants pointed out as either contributing to or detracting from a Rewind's believability.

\subsubsection{GPS Usage}
% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
% GPS - 69%, non-GPS - 81%
Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did in terms of percentage. Differences in Rewinds believability is statistically significant $\chi^2(1, N=128) = 2.917$, $p <.05$). Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them. The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations. Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations. Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory. So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory. One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving. I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.

Our results show that GPS usage influences what features participants pick out when deciding whether Rewinds are accurate reflections of their own memories of their trips. When we split the responses of regular GPS users from the other participants' responses, we saw that GPS users looked at signs in the Rewind the most to determine accuracy. Participants who were not regular GPS users cited the route and surrounding landmarks as features which made the Rewind believable as memories.

\subsubsection{Frequent Travelers}
% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
% frequent - 86%, non-frequent - 65%

\subsubsection{Travel Companions}
% significant effects on photo/location belivability $\chi^2(1,91) = 20.956$, p < 0.01
% traveling alone - 82%, not alone - 25%
% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(1,127) = 1.865$, p = 0.086(< 0.1)
% traveling alone - 84%, not alone - 72%
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$. The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.

\subsubsection{Distance}
% no ignificant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(5,128) = 10.093$, p = 0.0726(< 0.1)
% 0 - 100%, 1 - 75%, 2 - 75%, 3 - 85%, 4 - 80%, 5 - 33%

\subsubsection{Visit Frequency}
% significant effects on photo belivability if we use alpha = 0.1 - $\chi^2(1,61) = 2.012$, p = 0.078(< 0.1)
% most frequently visited location - 71%, least frequently visited location - 89%
% no significant effects on video/trip belivability $\chi^2(1,91) = 0.951$, p = 0.1647(> 0.05)
% trip that include most frequently visited locations  -  70%, trip that include least frequently visited locations - 81%
We found that the more visits a location had, the less likely it was for the Rewind associated with it to be judged as accurate by the participant. Trips with a location that was visited most frequently by the participant were said to be accurate 75\% of the time. The more a person visits a location, the more they may notice inconsistencies between the actual place and a digitally-fabricated memory of it. Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.

\subsubsection{Other Variables}
To get a better understanding of what the important features of locational memories are, we looked at participants' responses to why they thought a Rewind was or was not accurate to their memory. Participants attributed the accuracy of a Rewind to the presence of different man-made structures. The most highly occurring answers to why a Rewind was accurate were: the route, the highways, roads, and streets, the signs, the landmarks, and the buildings. The reasons why a Rewind did not seem accurate to participants' memories included more temporal and environmental features. When participants responded that a Rewind was not accurate to their memory, they cited the streets, the season and foliage, the time of day, and the angle the Rewind viewed the world at as factors of inaccuracy.

@@

\subsubsection{Travel Companions}
% no significant effects on photo desirability $\chi^2(1,94) = 0.071$, p = 0.3948(> 0.05)
% significant effects on video/trip desirability if alpha = 0.1 - $\chi^2(1, 133) = 2.443$, p = 0.059(< 0.1)
% alone - 13%, not alone - 26%

>>>>

% heather - need to be rephrased perhaps? Should we give a high level summary of all the relationships we've found? More analysis to be done for photo vs. videos, another table?
% semantic vs episodic memory
% mention distance categories in the beginning (up up up) + everything else 
\section{Findings}
The findings of our user study center on the participants’ relationships to the Rewinds generated from their location data compared to the static photos. We focus on the participants’ judgments of their Rewinds’ memorability, believability, and desirability in comparison to their judgments of the photos. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, which we defined as people who use GPS navigation even in locations already familiar to them.

Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters; and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

@@

\section{Memorability}
Rewinds, and digitally-mediated memories in general, are meant to engage a person's memory. To find out what features make a digital memory memorable, we examined participant responses to whether they were able to remember the location in a photo or recall the trip in a Rewind. Photo memorability is determined by whether or not the participant remembered the location depicted. Because a Rewind contains many locations, it would be unfair to evaluate its memorability based on whether the participant remembers any locations portrayed. So, Rewind memorability is determined by whether the participant remembered and could distinguish the particular trip taken. In this section, we look at differences in photo and Rewind memorability based on our five metrics.

% h - deleted participants # for consistencies - P4, P6 and P10 for future reference
\subsubsection{Rewinds vs. Static Photos} 
Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p < .01$). When presented with a photo, participants were able to recognize the depicted location 49.7\% of the time. Recognition rate of locations reached 96.6\% when participants were shown Rewinds. As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues. Three participants (P4, P6, and P10) who were unable to recall a location from a static photo remembered the location only after seeing the accompanying Rewind. They expressed contentment after watching the Rewind, proclaiming ``I recognize the photo now!''
%TODO h - add another table, only abt memorability tho

\subsubsection{Distance}
%TODO  where is home? need to explain this part in system? make sure this is explained
% only affect location rememberance
% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.

For photos, as the distance increased, memorability decreased, suggesting that locations farther away from home were less likely to be remembered. In Distance Group 0, or the participant's home location, location recall was 100\%. One participant, upon recognition, explained that she knew the location because ``my husband's car is in the driveway.'' By Distance Group 5, which represented the locations farthest away from home, remembrance was down to 10\%. These percentages are statistically significant, with a p-value of 0.0028.

%TODO find citation that humans travel most within x km of their home/work nodes
%TODO memory competition--similar memories compete for significance
For Rewind memorability, there was no statistical significance. Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except in Distance Group 1. Remembrance for all distance groups was between 50--60\%, but was 25\% in Distance Group 1. This data suggests that participants often could not distinguish the exact trips that occurred in locations close to their home. This is where most trips happen, so competition between similar memories would make it harder to distinguish the specific trip that generated the Rewind.

@@

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
% Differences in photo memorability due to visit frequency were statistically significant, while differences in location memorability were not. Photo memorability is higher for locations that are most frequently visited by the participant, with a remembrance rate of 72.3\%. Photo remembrance rate for the least frequently visited locations is 35.8\%. This is statistically significant at $\chi^2(1,128) = 14.458$, $p < 0.01$.

Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\%, $\chi^2(1, N=20) = 3.215$, $p < .05$. In least frequently visited locations, Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p < .01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our findings suggest that the presence of travel companions increases likelihood of Rewind remembrance. Rewinds depicting trips where participants believed they were traveling alone had a remembrance rate of 62\%, while trips where participants had a traveling companion were remembered 90\% of the time, $\chi^2(1, N=133) = 9.016$, $p < .01)$. One participant recalled a particular trip because ``I remembered my friend and I walked a certain way--I don't usually take this route.'' Another participant recalled that ``I went out with roommates to a bar. We took a weird route, different from my usual route."

\subsubsection{Frequent Travelers}
% has no siginifant effects on location no trip rememberance
% needing explaination perhaps?
We found no statistically significant effect on photo and Rewind memorability from participants' identification as frequent travelers.

\subsubsection{GPS Usage}
Our findings suggests that Rewinds, rather than photos, may be a more suitable form of digital memory for GPS users. Remembrance of Rewinds was higher than remembrance of photos for regular GPS users by a difference of 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$. There was no significant difference between photo remembrance and Rewind remembrance in non-regular GPS users.
% h - prob explain this a little bit more
% Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance. (GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - come back to this if time allows
% because memories are simply not encoded so there's no way to retrieve it in the first place?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our findings show that GPS usage significantly affected photo remembrance (Table 2), but not Rewind remembrance. Non-regular GPS users recalled the location in a photo 58\% of the time whereas regular GPS users recalled the location 33\% of the time. A regular GPS user mentioned during the study that ``I don't really pay attention to my surroundings when I'm driving. I'm focused on the GPS and the road.''

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Believability}
Rewinds should be believable as digitally-sourced memories, so we define the believability of a Rewind as its accuracy to the participant's memories. For distance and visit frequency, we found no statistically significant results, but in addition to our five metrics, we solicited other factors that affected a photo or Rewind's believability from participants.

%\subsubsection{Distance}
% no ignificant effects on photo/location belivability $\chi^2(5,86) = 7.745$, p = 0.1709 (> 0.05)
% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(5,128) = 10.093$, p = 0.0726(< 0.1)
% 0 - 100%, 1 - 75%, 2 - 75%, 3 - 85%, 4 - 80%, 5 - 33%

%\subsubsection{Visit Frequency}
% significant effects on photo belivability if we use alpha = 0.1 - $\chi^2(1,61) = 2.012$, p = 0.078(< 0.1)
% most frequently visited location - 71%, least frequently visited location - 89%
% no significant effects on video/trip belivability $\chi^2(1,91) = 0.951$, p = 0.1647(> 0.05)
% trip that include most frequently visited locations  -  70%, trip that include least frequently visited locations - 81%
%We found that the more visits a location had, the less likely it was for the Rewind associated with it to be judged as accurate by the participant. Trips with a location that was visited most frequently by the participant were said to be accurate 75\% of the time. The more a person visits a location, the more they may notice inconsistencies between the actual place and a digitally-fabricated memory of it. Trips with a location that was visited least frequently had a higher accuracy rating of 82\%.

\subsubsection{Travel Companions}
% significant effects on photo/location belivability $\chi^2(1,91) = 20.956$, p < 0.01
% traveling alone - 82%, not alone - 25%
% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(1,127) = 1.865$, p = 0.086(< 0.1)
% traveling alone - 84%, not alone - 72%
Our findings show that in both photos and Rewinds, believability was higher when participants were traveling alone. For photos, the difference in believability between those traveling alone and those traveling with company was 37\%, $\chi^2(1, N=82) = 5.137$, $p < .05$. For Rewinds, the difference was 12\%, $\chi^2(1, 127) = 1.865$, $p = 0.086 (<.1)$. The smaller difference suggests that Rewinds are more believable than photos for trips taken with company.

\subsubsection{Frequent Travelers}
% no significant effects on photo belivability $\chi^2(1,86) = 0$, p = 0.4947(> 0.05)
% significant effects on video belivability $\chi^2(1,128) = 5.837$, p = 0.0079 (< 0.01)
% frequent - 86%, non-frequent - 65%
Participants who identified as frequent travelers found 86\% of Rewinds believable and accurate to their memory, while non-frequent travelers found 65\% of Rewinds believable, $\chi^2(1, 128) = 5.835$
$p < .05$. This suggests that Rewinds would be more suitable for a particular type of person.

\subsubsection{GPS Usage}
% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
% GPS - 69%, non-GPS - 81%
Our results show that participants who were non-regular GPS users found Rewinds believable more often than regular GPS users, suggesting the appropriate audience for Rewinds. Regular GPS users found Rewinds believable 69\% of the time, while non-regular users found Rewinds believable 84\% of the time, $\chi^2(1, 128) = 2.917$, $p < .05$.

\subsubsection{Other factors}
Participants attributed the accuracy of a Rewind to the presence of different man-made structures. The most highly occurring answers to why a Rewind was accurate were: the route, the highways, roads, and streets, the signs, the landmarks, and the buildings. The reasons why a Rewind did not seem accurate to participants' memories included more temporal and environmental features: the season and foliage, the time of day, and the angle of view. One participant said that ``things look a little odd. It's too bright for the time of day,'' and another insisted ``it should be night.''

@@

\subsubsection{Travel Companions}
% no significant effects on photo desirability $\chi^2(1,94) = 0.071$, p = 0.3948(> 0.05)
% significant effects on video/trip desirability if alpha = 0.1 - $\chi^2(1, 133) = 2.443$, p = 0.059(< 0.1)
% alone - 13%, not alone - 26%
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$. The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.
